Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-13 cosmic_voids.tex
re-ordenando graficas

  \captionof{figure}{\small Physical internal properties of voids for 
  the two finding scheme. Density field (left panels), radial-projected
  velocity field (middle panels) and FA field (right panels). The analysis
  is performed for both, subcompensated (first two rows) and overcompensated
  voids (last two rows).}
  \label{fig:RhoVel}
  \vspace{0.1 cm}
\end{figure*}

\begin{figure*}
\centering  
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_VwebFAG1.pdf}
  \captionof{figure}{\small Physical internal properties of voids for 
  the two finding scheme. Density field (left panels), radial-projected
  velocity field (middle panels) and FA field (right panels). The analysis
  is performed for both, subcompensated (first two rows) and overcompensated
  voids (last two rows).}

  \label{fig:RhoVel}
  \vspace{0.1 cm}

\end{figure*}

\begin{figure*}
\centering  
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_VwebFAG1.pdf}

  \captionof{figure}{\small Physical internal properties of voids for 
  the two finding scheme. Density field (left panels), radial-projected
  velocity field (middle panels) and FA field (right panels). The analysis
  is performed for both, subcompensated (first two rows) and overcompensated
  voids (last two rows).}

  \label{fig:RhoVel}
  \vspace{0.1 cm}

>>>>

  \captionof{figure}{\small Spherically averaged radial density profile for
    voids. The sample is split into subcompensated and overcompensated voids
    (right and left) for the web schemes T-Web and V-Web (top and
    bottom).}
  \label{fig:density_profile}
  \vspace{0.1 cm}
\end{figure*}

\begin{figure*}
\centering  
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_VwebFAG1.pdf}
  \captionof{figure}{\small Spherically averaged radial velocity profile for
    voids. The sample is split into subcompensated and overcompensated voids
    (right and left) for the web schemes T-Web and V-Web (top and
    bottom).}
  \label{fig:velocity_profile}
  \vspace{0.1 cm}
\end{figure*}

\begin{figure*}
\centering  
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_VwebFAG1.pdf}

  \captionof{figure}{\small Spherically averaged Fractional Anisotropy
    profile for voids. The sample is split into subcompensated and
    overcompensated voids  (right and left) for the web schemes T-Web and V-Web (top and  bottom).}
  \label{fig:FA_profile}
  \vspace{0.1 cm}
